$titulo$

### 2024-08-12 templates/propuestatemplate.tex
tmpl.2

\documentclass[
  journal=large,
  manuscript=article-type,
  year=2020,
  volume=37,
]{cup-journal}

@@

\keywords{keyword entry 1, keyword entry 2, keyword entry 3} %% First letter not capped

@@

\begin{abstract}
$introduccion$
\end{abstract}

\noindent $resumen$

@@

\section{Conclusion}
The conclusion text goes here.

\begin{acknowledgement}
Insert the Acknowledgment text here.
\end{acknowledgement}

@@

>>>>

\documentclass[
  journal=large,
  manuscript=propuesta,
  year=2020,
  volume=37,
]{cup-journal}

@@

\keywords{$palabrasclave$} %% First letter not capped

@@

\begin{abstract}
$resumen$
\end{abstract}

\noindent $introduccion$

@@

\section{Conclusion}
$concusion$

\begin{acknowledgement}
$agradecimiento$
\end{acknowledgement}

@@

$apendice$
